\documentclass[10pt, letterpaper]{moderncv}

\usepackage{textcomp}
\usepackage{ifthen}
\usepackage{lastpage}
\usepackage{ragged2e}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\moderncvtheme[purple]{classic}

\setlength{\makecvtitlenamewidth}{12cm}
\renewcommand*{\namefont}{\fontsize{24}{29}\mdseries\upshape}
\name{Petter Fredrik}{Hemnes}
\title{Résumé}

\email{phemnes@gmail.com}


\mobile{+47-91-56-34-91}

\homepage{petterhemnes.herokuapp.com/blog/}

\social[github]{prayanthem}

\social[linkedin]{petter-fredrik-hemnes}





\begin{document}
\rfoot{\ifthenelse{\value{page}=1}{}{\addressfont\itshape\textcolor{gray}{\thepage}}}
% Letter Information
\recipient{Wile E. Coyote}{ACME Corporation for Making Explosions, Inc \\ Nowhere, NK}
\date{\today}
\opening{Please don't eat me!}
\closing{Meep meep,}
\enclosure[Attached]{r\'{e}sum\'{e}} % List of enclosed documents

\makelettertitle            % Print letter title
    I would like to become a Test Subject at your company.

    I know that
        ACME
    is one of the leading explosives manufacturers in the world.

\input{"C:/Users/taplop/Code/resume/resume/templates/latex/letter_templates/analysis"}


Thank you for taking the time to review my application.

\makeletterclosing          % Print letter signature
\newpage
\setcounter{page}{1}
\justifying

\rfoot{\addressfont\itshape\textcolor{gray}{\ifthenelse{\value{page}=1}{\\\small updated 2018--12--09}{\thepage\\\small updated 2018--12--09}}}

\makecvtitle
\vspace{-20pt}


          \cvitem{
      Interests%
      }{Business analytics, econometrics, space, automation}

          \cvitem{
      Citizenship%
      }{Norway}


\section{Education}
    \begin{samepage}
      \cventry
          {2016--2021 (present)}
          {\href{https://www.nhh.no/en/study-programmes/msc-in-economics-and-business-administration/business-analytics/}{%
             MSc in Economics and Business Administration%
}}
          {\href{https://nhh.no}{%
             Norwegian School of Economics%
}}
          {}
          {Bergen, Norway%
}
        {\begin{itemize}
             \item{Specialized in Business Analytics}
             \item{Undergraduate exchange at Rikkyo (St. Pauls) University, Tokyo, Japan}
             \item{Graduate exchange at National University of Singapore}
         \end{itemize}}
    \end{samepage}
    \begin{samepage}
      \cventry
          {2019--2021}
          {%
             Master's in international management%
}
          {\href{https://www.nhh.no/en/for-students/international-opportunities/cems-mim/}{%
             NHH CEMS - the global alliance in management education%
}}
          {}
          {Bergen, Norway%
}
        {\begin{itemize}
             \item{CEMS semester abroad at National University of Singapore}
         \end{itemize}}
    \end{samepage}


\section{Co-op experience}
    \begin{samepage}
      \cventry
          {Jan 2018 - March 2018}
          {Global volunteer}
          {%
%
AIESEC in Xi'an%
}
          {Xi'an, China}
        {}
        {
            \begin{itemize}
                \item{English teaching at rural primary schools.}
                \item{Autism support worker}
                \item{Team leader of the twenty volunteers}
            \end{itemize}
        }
    \end{samepage}
      %\vspace{10pt}
    \begin{samepage}
      \cventry
          {Sep 2015 - May 2016}
          {Shop assistant}
          {%
%
REMA1000%
}
          {Oslo, Norway}
        {}
        {
            \begin{itemize}
                \item{Cashier worker, restocking and storage management}
            \end{itemize}
        }
    \end{samepage}
      %\vspace{10pt}
    \begin{samepage}
      \cventry
          {Summer 2013 - 2016}
          {Fisherman}
          {%
%
Wetterøy Partsreder%
}
          {Bodø, Norway}
        {}
        {
            \begin{itemize}
                \item{Used manual and automatic fishing rods to catch marine life.}
                \item{Delivered on average 100 kilos of cod every working day.}
            \end{itemize}
        }
    \end{samepage}
      %\vspace{10pt}
    \begin{samepage}
      \cventry
          {Summer 2014-2015}
          {Municipality worker}
          {%
Helligvær
, %
Bodø Municipality%
}
          {Bodø, Norway}
        {}
        {
            \begin{itemize}
                \item{Municipality property maintainance}
                \item{Garbage disposal}
                \item{Support of the elderly}
            \end{itemize}
        }
    \end{samepage}
      %\vspace{10pt}
  %\vspace{-10pt}


\section{Projects}
          \cvlistitem{Online analytics web application for the Norwegian market of secondhand cars.}


\section{Relevant coursework}
    \cvlistdoubleitem{Financial accounting}{Managerial accounting}
    \cvlistdoubleitem{Managerial economics}{Strategic financial management}
    \cvlistdoubleitem{Quantitative and computing methods}{Empirical methods}
    \cvlistdoubleitem{Statistics for economists}{}


\section{Technical skills}
          \cvlistitem{Python (django), Java, R, stata, \LaTeX}

          \cvlistitem{Microsoft Windows (XP to 10), Linux (Ubuntu)}

          \cvlistitem{Visual studio, Git, Photoshop, LibreOffice, Microsoft Office}


\section{Languages}
          \cvitem{
      Fluent%
      }{Norwegian, English}

          \cvitem{
      Intermediate%
      }{Japanese}

          \cvitem{
      Beginner%
      }{Spanish}




\end{document}
